---
title: R in 3 Months Week 11 (Advanced Data Viz, Part 2)
format:
  rfortherestofus-slides-revealjs:
    menu: false
    progress: true
    slide-number: true
    show-slide-number: print
    center: true
    incremental: true
    auto-animate: true
execute: 
  message: false
  warning: false
  cache: false
  # eval: false
  echo: true
title-slide-attributes:
  data-background-image: assets/rru-hex-bg-gradient-dark.svg
  data-background-size: cover
editor_options: 
  chunk_output_type: console
countdown:
  color_background: "lightblue"
  border_width: "0"
---

```{r}
#| echo: false
library(tidyverse)
library(janitor)
```


# Agenda

1. Housekeeping

1. Advanced Custom Themes

1. Mapping

1. Interactive Data Viz

1. Next Week

::: {.notes}
https://rin3spring2026.rfortherestofus.com/slides/slides-week-11.html
:::

# Housekeeping

1. Two more weeks: Advanced Quarto and final projects

1. Final project is to record a video demonstrating something you've learned ([lesson](https://rfortherestofus.com/courses/r-in-3-months-spring-2026/lessons/spring-2026-r-in-3-months-final-project))

::: {.notes}
Please submit things!
:::

## Self-reflection
{{< countdown "1:00" top=0 right=0 >}}

**Please share in the chat:**  

1. What was one thing that you've found difficult this week?  
2. What was one thing that you've learned this week?  

## Why is `group = district` needed?

{{< countdown "1:00" top=0 right=0 >}}

```{r eval = FALSE, echo = TRUE}
ggplot(
  aes(
    x = year,
    y = pct,
    color = highlight_district,
    group = district
  )
) +
  geom_line()
```


A. To create one line per district  
B. To color the lines  
C. To remove missing values  
D. To format percentages  

## Why is `group = district` needed?

```{r eval = FALSE, echo = TRUE}
ggplot(
  aes(
    x = year,
    y = pct,
    color = highlight_district,
    group = district
  )
) +
  geom_line()
```


A. [To create one line per district]{.mark}  
B. To color the lines  
C. To remove missing values  
D. To format percentages 



# Advanced Custom Themes {.inverse}



# Organizations with Public Custom {ggplot2} Themes 

* [The BBC's {bbplot} Package](https://github.com/bbc/bbplot)  

* [The BBC's Cookbook for R Graphics](https://bbc.github.io/rcookbook/) 

* [Washington Soil Health Initiative {washi} Branding Package](https://wa-department-of-agriculture.github.io/washi/)  

# Organizations with Public Custom {ggplot2} Themes, Continued 

* [Sage Bionetworks {sagethemes} Package](https://sage-bionetworks.github.io/sagethemes/)

* [Duke University's {duke} Package](https://aidangildea.github.io/duke/)

* [University of Exeter's `theme_exeter()`](https://github.com/lukepilling/theme_exeter)

::: {.notes}
https://book.rfortherestofus.com/themes.html

- Add hide_gridlines
- Add hide_legend
:::

# Mapping {.inverse}

::: {.notes}
https://book.rfortherestofus.com/maps.html

https://r.geocompx.org/

- geometry type
- dimensions
- bounding box
- crs
- geometry column
:::

## Check-in break

{{< countdown "2:00" top=0 right=0 >}}

```{r eval = FALSE, echo = TRUE}
ggplot() +
  geom_sf(
    data = portland_boundaries,
    fill = "gray80"
  ) +
  geom_sf(
    data = traffic_signals,
    aes(color = software_type),
    size = 1
  )
```

1. Which layer will appear underneath the other?
2. What geometry type is `traffic_signals` likely using?
3. What will determine the color of the traffic signal points?

::: {.notes}
1. First layer (portland_boundaries) draws underneath.
2. traffic_signals is likely _point_ geometry.
3. software_type controls color.
:::


# Interactive Data Viz {.inverse}

::: {.notes}
https://davidgohel.github.io/ggiraph/
:::

# Next Week

- Advanced Quarto

- Do the lessons relevant to you (chat with Gracielle if you'd like help identifying them) and skip the rest

- I'll demonstrate parameterized reporting next week in the live session so feel free to skip those lessons for now

- Start to think about final project
