---
title: R in 3 Months Week 13 (Wrapping Up)
format:
  rfortherestofus-slides-revealjs:
    menu: false
progress: true
slide-number: true
show-slide-number: print
center: true
incremental: true
auto-animate: true 
execute: 
  message: false
  warning: false
  cache: false
  # eval: false
  echo: true
title-slide-attributes:
  data-background-image: assets/rru-hex-bg-gradient-dark.svg
data-background-size: cover
editor:
  render-on-save: true
editor_options: 
  chunk_output_type: console
---

```{r}
#| echo: false
library(tidyverse)
library(janitor)
```

# Agenda

1.  How Far You've Come

2.  Where to Go From Here

3. How to Ask Good (Code) Questions

4. Wrapping Up

::: notes
https://rin3fall2025.rfortherestofus.com/slides/slides-week-13.html
:::

# How Far You've Come {.inverse}

```{r}
#| echo: false

library(googlesheets4)
library(tidyverse)
library(janitor)
library(scales)

rin3_start_date <- "2025-08-01"

gs4_auth("gracielle@rfortherestofus.com")

pre_survey <- read_sheet(
  "https://docs.google.com/spreadsheets/d/19Ny92IGg0ZzIqiLs7QywaGF-Y85HQZn1iIIXN4I_tpg/edit#gid=1201619159"
) |>
  clean_names() |>
  filter(timestamp > as_date(rin3_start_date)) |>
  select(-what_is_your_name)

pre_survey_tidy <-
  pre_survey |>
  select(contains("rate"), contains("terrified")) |>
  set_names(c("data_analysis", "visualization", "scared")) |>
  pivot_longer(cols = everything()) |>
  mutate(timing = "Pre")

post_survey <- read_sheet(
  "https://docs.google.com/spreadsheets/d/1S5g1UYyBKiUfIU3yi9M_OZs1RvedH5xPPrMhs8Sw53o/edit#gid=1400508795"
) |>
  clean_names() |>
  filter(timestamp > as_date(rin3_start_date))

post_survey_tidy <-
  post_survey |>
  select(contains("rate"), contains("terrified")) |>
  set_names(c("data_analysis", "visualization", "scared")) |>
  pivot_longer(cols = everything()) |>
  mutate(timing = "Post")

pre_post_data <-
  bind_rows(pre_survey_tidy, post_survey_tidy) |>
  group_by(timing, name) |>
  summarize(avg_response = mean(value, na.rm = TRUE)) |>
  ungroup() |>
  mutate(timing = fct_rev(timing)) |>
  mutate(avg_response_formatted = number(avg_response, accuracy = 0.1))

pre_post_plot <- function(area) {
  pre_post_data |>
    filter(name == area) |>
    ggplot(aes(
      timing,
      avg_response,
      color = timing,
      group = 1,
      label = avg_response_formatted
    )) +
    geom_line(color = "grey") +
    geom_point(size = 10) +
    geom_text(color = "white") +
    theme_minimal(base_family = "Inter") +
    theme(
      panel.grid.minor = element_blank(),
      axis.title = element_blank(),
      legend.position = "none"
    ) +
    scale_y_continuous(limits = c(1, 10), breaks = seq(1, 10, 1)) +
    scale_color_manual(values = rev(c("#6cabdd", "#ff7400")))
}
```

::: {.notes}
https://rfortherestofus.com/courses/r-in-3-months-fall-2025/lessons/r-in-3-months-progress-survey
:::

## Data Analysis

```{r}
#| echo: false
pre_post_plot(area = "data_analysis")
```

## Data Visualization

```{r}
#| echo: false
pre_post_plot(area = "visualization")
```

## How Scared/Excited You Are About R

```{r}
#| echo: false
pre_post_plot(area = "scared")
```

## What You've Done in the Last Three Months {.inverse}

::: {.notes}
https://docs.google.com/presentation/d/1hDWjd-E2JLnVrRYF4l8VZSWqUIDrj49TTJwzu4hgx_I/edit?usp=sharing
:::

# Where to Go From Here {.inverse}

## Rubber Duck Debugging

The power of talking through your code problems 🦆 💬

-   It doesn't have to be a duck
  
-   Walk through as if the "duck" has no context


## Planning with Pseudo Code

-   Use plain language **before** you code (sometimes this means starting by the end)

-   Get to know your subject qualitatively

-   Refine your analysis questions


## Break it down!

-   Split your code into multiple R scripts by themes and outputs

-   Save functions in separate R scripts

-   Bring to your Quarto document only what you need


## Where to Ask Questions {.inverse}

---

There are two popular question and answer communities for (R) code questions:

---

### [Posit Community](https://community.rstudio.com/)

-   This community is run by Posit and is specifically for R users

-   The admins do work to make the site a welcoming place for all users

---

### [Data Science Learning Community](https://dslc.io/)

-   Slack community that is very welcoming to newbies

-   Has regular office hours where you can get 1-on-1 help

---

### Bonus: [R-Ladies+](https://rladies.org/)

-   "A worldwide organization whose mission is to promote gender diversity in the R community"

-   Extremely welcoming

-   Have local chapters that often host events, and many are online

---


### Bonus: Social Media

- [Bluesky](https://bsky.app/search?q=%23rstats)

- [LinkedIn](https://www.linkedin.com/search/results/all/?keywords=%23rstats&origin=GLOBAL_SEARCH_HEADER&sid=2iI)


---

### Bonus: Conferences

- [posit::conf](https://posit.co/conference/)

- [useR Conference](https://user2026.r-project.org/)

- [Cascadia R Conf](https://cascadiarconf.com/)

- [R Medicine Conference](https://rconsortium.github.io/RMedicine_website/)

- [rainbowR virtual conference](https://rainbowr.org/)

- [Jumping Rivers list of R conferences and events](https://jumpingrivers.github.io/meetingsR/events.html)

<!--- - [NYC/DC/Dublin R Conference](https://rstats.ai/) --->

---

### Bonus: AI {.inverse}

{{< video https://cdn.muse.ai/w/0dc8f6b8d6cd7bea6de83fb6083cb05629c787e47607c2b77150dd74f4dd2ffa/videos/video.mp4 >}}

::: {.notes}
Show Positron assistant fix and explain video
:::

# How to Ask Good (Code) Questions {.inverse}

## How to Ask Good (Code) Questions

The most important part of asking good questions about code is to provide **reproducible examples**.

. . .

> A **reproducible example** contains all necessary code to reproduce your error or to customise your chart.

. . .

The `reprex` package is designed to help guarantee your examples are reproducible.

## Examples are *Minimal*

In addition to making your code reproducible you should try to make it *minimal*.

. . .

> Use the smallest, simplest, most built-in data possible.
>
> Think: ~~iris~~ palmerpenguins or mtcars. Bore me.

. . .

Make your question as focused as possible

## Example of a Good Reprex 

How can I reorder bars on the y axis?

## Using the `reprex` Package

1.  Select the code that makes your reprex

2.  Open the Addins menu and select "Render reprex..."

3.  Choose the options for where you're asking your question

4.  Copy and paste the output in the Viewer tab into your question

## Learn More About Reprex

- [Jenny Bryan video overview of reprex](https://www.youtube.com/watch?v=5gqksthQ0cM&ab_channel=PositPBC)

- [StackOverflow thread on how to write a good reprex](https://stackoverflow.com/questions/5963269/how-to-make-a-great-r-reproducible-example/16532098)

# Wrapping Up {.inverse}

## R in 3 Months

1.  Submit any assignments for feedback any time in December

2.  Any 1-on-1s with Gracielle must be completed by end of December

3.  Please submit final assignments whenever (we love seeing what you've done!)

4.  You have access to course materials FOREVER

## Other Things

1. Topics courses (use coupon code RIN3TOPICSCOURSES to get 25% off)

1. Everyone has access to [Using Git and GitHub with R](https://rfortherestofus.com/courses/git-github)

1. Additional ways that R for the Rest of Us can help you and your organization

::: {.notes}
https://rfortherestofus.com/training

https://rfortherestofus.com/consulting
:::

# Thank You for Being Part of R in 3 Months! {.inverse}
